An inventory of human light exposure related behaviour

### 2023-11-09 manuscript_SciRep.Rmd
Technical check completed-MASj

# author: 
#   - name          : "Mushfiqul Anwar Siraji"
#     affiliation   : "1, *"
#     email         : "mushfiqul.anwarsiraji@monash.edu"
#     role:         
#       - Formal Analysis
#       - Visualization
#       - Writing – original draft
#       - Writing – review & editing
#        
#   - name          : "Rafael Robert Lazar"
#     affiliation   : "2, 3, *"
#     role:
#       - Data curation
#       - Investigation
#       - Project administration
#       - Visualization
#       - Writing – original draft
#       - Writing – review & editing
#       
#   - name          : "Juliëtte	van Duijnhoven"
#     affiliation   : "4, 5"
#     email         : "j.v.duijnhoven1@tue.nl"
#     role:         
#       - Conceptualization
#       - Methodology
#       - Investigation
#       - Writing – review & editing
# 
#   - name          : "Luc Schlangen"
#     affiliation   : "5, 6"
#     email         : "l.j.m.schlangen@tue.nl"
#     role:         
#       - Conceptualization
#       - Methodology
#       - Investigation
#       - Writing – review & editing
# 
#   - name          : "Shamsul Haque"
#     affiliation   : "1"
#     email         : "shamsul@monash.edu"
#     role:         
#       - Conceptualization
#       - Supervision
#       - Writing – review & editing
#       
#   - name          : "Vineetha Kalavally"
#     affiliation   : "7"
#     email         : "vineetha@monash.edu"
#     role:         
#       - Supervision
#       - Writing – review & editing
#       
#   - name          : "Céline Vetter"
#     affiliation   : "8"
#     email         : "celine.vetter@colorado.edu"
#     role:         
#       - Conceptualization
#       - Writing – review & editing
#       
#   - name          : "Gena Glickman"
#     affiliation   : "9"
#     email         : "gena.glickman@usuhs.edu"
#     role:         
#       - Conceptualization
#       - Methodology
#       - Writing – review & editing
#       
#   - name          : "Karin Smolders"
#     affiliation   : "5,6"
#     email         : "k.c.h.j.smolders@tue.nl"
#     role:         
#       - Conceptualization
#       - Methodology
#       - Writing – review & editing
# 
#   - name          : "Manuel Spitschan"
#     corresponding : yes
#     affiliation   : "10, 11, 12"
#     email         : "manuel.spitschan@tum.de "
#     role:         
#       - Conceptualization
#       - Data curation
#       - Investigation
#       - Project administration
#       - Visualization
#       - Methodology
#       - Writing – original draft
#       - Writing – review & editing
# 
# affiliation:
#   - id            : "1"
#     institution   : "Monash University, Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia"
#   - id            : "2"
#     institution   : "Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland"
#   - id            : "3"
#     institution   : "University of Basel, Transfaculty Research Platform Molecular and Cognitive Neurosciences, Basel, Switzerland"
#   - id            : "4"
#     institution   : "Eindhoven University of Technology, Department of the Built Environment, Building Lighting, Eindhoven, Netherlands"
#   - id            : "5"
#     institution   : "Eindhoven University of Technology, Intelligent Lighting Institute, Eindhoven, Netherlands"
#   - id            : "6"
#     institution   : "Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Human-Technology Interaction, Eindhoven, Netherlands"
#   - id            : "7"
#     institution   : "Monash University, Department of Electrical and Computer Systems Engineering, Selangor, Malaysia"
#   - id            : "8"
#     institution   : "University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA"
#   - id            : "9"
#     institution   : "Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA"   
#   - id            : "10"
#     institution   : "Translational Sensory & Circadian Neuroscience, Max Planck Institute for Biological Cybernetics, Tübingen, Germany"
#   - id            : "11"
#     institution   : "TUM School of Medicine and Health, Technical University of Munich, Munich, Germany"
#   - id            : "12"
#     institution   : "TUM Institute of Advanced Study (TUM-IAS), Technical University of Munich, Garching, Germany"
#   - id            : "*"
#     institution   : "Joint first author"   
# 
# 
# authornote: |
#   This research is supported by funding from the Welcome Trust (204686/Z/16/Z), the European Training Network LIGHTCAP (project number 860613) under the Marie Skłodowska-Curie actions framework H2020-MSCA-ITN-2019, the BioClock project (number 1292.19.077) of the research program Dutch Research Agenda: Onderzoek op Routes door Consortia (NWA-ORC) which is (partly) financed by the Dutch Research Council (NWO), and the European Union and the nationals contributing in the context of the ECSEL Joint Undertaking programme (2021-2024) under the grant #101007319.

@@

documentclass     : "apa6"
classoption       : "man"
output            : 
  papaja::apa6_pdf:
    keep_tex: true
    latex_engine: xelatex
    includes:
      in_header: header.tex
header-includes:
  - \usepackage{rotating}
  - \DeclareDelayedFloatFlavor{sidewaysfigure}{figure}

mainfont: Arial
---

>>>>

author:
  - name          : "Mushfiqul Anwar Siraji"
    affiliation   : "1, 2,+"
    email         : "mushfiqul.anwarsiraji@monash.edu"
    role:
      - Formal Analysis
      - Visualization
      - Writing – original draft
      - Writing – review & editing

  - name          : "Rafael Robert Lazar"
    affiliation   : "3, 4, +"
    role:
      - Data curation
      - Investigation
      - Project administration
      - Visualization
      - Writing – original draft
      - Writing – review & editing

  - name          : "Juliëtte	van Duijnhoven"
    affiliation   : "5, 6"
    email         : "j.v.duijnhoven1@tue.nl"
    role:
      - Conceptualization
      - Methodology
      - Investigation
      - Writing – review & editing

  - name          : "Luc Schlangen"
    affiliation   : "6, 7"
    email         : "l.j.m.schlangen@tue.nl"
    role:
      - Conceptualization
      - Methodology
      - Investigation
      - Writing – review & editing

  - name          : "Shamsul Haque"
    affiliation   : "1"
    email         : "shamsul@monash.edu"
    role:
      - Conceptualization
      - Supervision
      - Writing – review & editing

  - name          : "Vineetha Kalavally"
    affiliation   : "8"
    email         : "vineetha@monash.edu"
    role:
      - Supervision
      - Writing – review & editing

  - name          : "Céline Vetter"
    affiliation   : "9"
    email         : "celine.vetter@colorado.edu"
    role:
      - Conceptualization
      - Writing – review & editing

  - name          : "Gena Glickman"
    affiliation   : "10"
    email         : "gena.glickman@usuhs.edu"
    role:
      - Conceptualization
      - Methodology
      - Writing – review & editing

  - name          : "Karin Smolders"
    affiliation   : "6,7"
    email         : "k.c.h.j.smolders@tue.nl"
    role:
      - Conceptualization
      - Methodology
      - Writing – review & editing

  - name          : "Manuel Spitschan"
    corresponding : yes
    affiliation   : "11, 12, 13, *"
    email         : "manuel.spitschan@tum.de "
    role:
      - Conceptualization
      - Data curation
      - Investigation
      - Project administration
      - Visualization
      - Methodology
      - Writing – original draft
      - Writing – review & editing

affiliation:
  - id            : "1"
    institution   : "Monash Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia"
  - id            : "2"
    institution   : "Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland"
  - id            : "3"
    institution   : "University of Basel, Transfaculty Research Platform Molecular and Cognitive Neurosciences, Basel, Switzerland"
  - id            : "4"
    institution   : "Eindhoven University of Technology, Department of the Built Environment, Building Lighting, Eindhoven, Netherlands"
  - id            : "5"
    institution   : "Eindhoven University of Technology, Intelligent Lighting Institute, Eindhoven, Netherlands"
  - id            : "6"
    institution   : "Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Human-Technology Interaction, Eindhoven, Netherlands"
  - id            : "7"
    institution   : "Monash University, Department of Electrical and Computer Systems Engineering, Selangor, Malaysia"
  - id            : "8"
    institution   : "University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA"
  - id            : "9"
    institution   : "Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA"
  - id            : "10"
    institution   : "Translational Sensory & Circadian Neuroscience, Max Planck Institute for Biological Cybernetics, Tübingen, Germany"
  - id            : "11"
    institution   : "TUM School of Medicine and Health, Technical University of Munich, Munich, Germany"
  - id            : "12"
    institution   : "TUM Institute of Advanced Study (TUM-IAS), Technical University of Munich, Garching, Germany"
  - id            : "+"
    institution   : "Joint first author"

  - id            : "13"
    institution   : "North South University, Department of History and Philosophy, Bangladesh"

  - id            : "*"
    institution   : "Corresponding Author"

authornote: |
  This research is supported by funding from the Welcome Trust (204686/Z/16/Z), the European Training Network LIGHTCAP (project number 860613) under the Marie Skłodowska-Curie actions framework H2020-MSCA-ITN-2019, the BioClock project (number 1292.19.077) of the research program Dutch Research Agenda: Onderzoek op Routes door Consortia (NWA-ORC) which is (partly) financed by the Dutch Research Council (NWO), and the European Union and the nationals contributing in the context of the ECSEL Joint Undertaking programme (2021-2024) under the grant #101007319.

@@

documentclass     : "apa6"
classoption       : "man"
output            : 
  papaja::apa6_pdf:
    keep_tex: true
    latex_engine: xelatex
    includes:
      in_header: header.tex
header-includes:
  - \usepackage{rotating}
  - \DeclareDelayedFloatFlavor{sidewaysfigure}{figure}
csl: "nature.csl"
mainfont: Arial
---
